Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-11-28 manuscript/si_template_2019.tex
cleanup appendix captions, toc

\item \textbf{Figure S5:} Importance plot for random forest variables

\item \textbf{Figure S6:} Characteristics of lakes with bathymetry versus non-bathymetry lakes

\item \textbf{Figure S7:} Lake characteristics comparison among shape and reservoir classes

\item \textbf{Figure S8:} Comparison between reported depth and bathymetry depth

@@

\begin{figure}
      \begin{center}
        \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Sensitivity analysis regarding different slope calculation methods.}\label{figS6}
    \end{figure}
\clearpage

>>>>

\item \textbf{Figure S5:} Lake geometry comparison among shape classes by depth and area

\item \textbf{Figure S6:} Effect of calculation technique on in-lake/nearshore slope comparison.

\item \textbf{Figure S7:} Importance plot for random forest variables

\item \textbf{Figure S8:} Characteristics of lakes with bathymetry versus non-bathymetry lakes

\item \textbf{Figure S9:} Lake characteristics comparison among shape and reservoir classes

\item \textbf{Figure S10:} Comparison between reported depth and bathymetry depth

\item \textbf{Table S1:} Summary of lake characteristics for the present study

\item \textbf{Table S2:} Effect of calculation technique on depth model fit and accuracy.

@@

\begin{figure}
      \begin{center}
        \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slope using different calculation techniques. See Table S2 for explanation of each.}\label{figS6}
    \end{figure}
\clearpage
